\setlength\parindent{0pt}

\chapter{Background Theory}

There are a large number of factors that determine the battery usage of a device. Some of them are system level, including brightness, hardware power consumption and operating system battery consumption, which are beyond the control of application developers. However there exist a large number of factors such as CPU usage, network usage, wakelocks, etc which developers can look into, to optimize. \\

CPU usage results from performing computations. CPU usage is of two types, foreground usage, i.e when the app is running in the foreground, and background usage, for when app is running in the background (to perform tasks such as synchronisation, download, checking for mails, messages, etc). While foreground CPU usage forms a major part of battery consumption by cpu, if unchecked, a lot of unnecessary computation and processing maybe happening in the background, leading to battery drain (Unnecessary computation and processing may be taking place in the foreground as well) \\

Network usage, including mobile network and WiFi also form a major portion of battery usage. Like CPU usage, network usage is also of two types, background and foreground. Also like CPU usage, the app may be sending and receiving unnecessary packets in the foreground, background, or both. This is a potential candidate in making an app battery heavy.\\

Wakelock is a feature, which when requested by an app, lets the app to prevent the phone from going to sleep, i.e. the app will run continuously.\cite{wakelock} Wakelocks are handled differently in iOS and Android. While Android provides more control to the developer to invoke and use wakelocks through partial wakelocks, which lets apps run in the background, executing tasks, regardless of screen state or display timeouts, iOS permits partial wakelocks only for VOIP and location services.\cite{stackoverflow} It is pretty evident that an app requesting for unnecessary wakelocks will have a high energy consumption.\\

There may be external factors in an app’s battery consumption, such as bluetooth usage, camera usage or some other function whose power consumption is not directly controllable by the app. Such factors cannot be handled by the developers of the app, and hence such factors will not be taken into account. There may also arise unanticipated bugs in the app which lead to battery drain. 