\setlength\parindent{0pt}

\chapter{Conclusion}

The internship majorly involved working in the field of automation. Technologies used during the course of the internship are as follows:
\begin{itemize}
	\item Shell Scripting
	\item Python Scripting
	\item Robot Framework
	\item UIAutomator
	\item Jenkins
\end{itemize}

In this project, a Battery Performance Test suite was developed, which performs detailed battery usage analysis of a given version of the given app. The suite is also capable of finding differenced in battery usage patterns for two given versions of the app. Further new test cases were added to the Functional Verification Test (FVT) suite which performed tests related to calendar and attachments. Existing test cases were modified to account for unforeseen popups and remove redundant checks.\\

To perform Battery Performance Tests, existing test cases for most common user interactions were shortlisted. The test cases were run and the usage patterns for the same were analysed using Battery Historian. Standalone Python scripts were developed for automation purposes as Battery Historian had to be run manually. One script was used to read the BatteryStats file and generate battery usage reports and the other script was used to compare battery usage reports for two given versions of the app. The entire worflow was automated by creating a Jenkins job.\\

The new test cases added to the FVT suite were converted from Java to Python as the Java library was no longer being used and the current suite uses Python UIAutomator. A total of 6 test cases were migrated from Java to Python. Watchers were also added to prevent unforeseen popups from breaking test cases and to eliminate checks for commonly occurring popups such as those asking for some confirmation.\\ 

The Battery Performance Test suite is capable of determining battery usage patterns for a given version, compare battery usage patterns of two version of the app and also find areas which are consuming battery unnecessarily. During the project, the test suite had found areas that need to be looked into to make the app more battery efficient which were fixed in later versions. The test suite will be run for every new version to gauge and compare battery usage patterns and to find battery consuming areas in newer versions as well. \\

The new test cases added are now part of the Functional Verification Test (FVT) suite and will be run whenever the FVT suite is run. Further the modified test cases are now easier to read and debug due to removal of redundant code sections. These test cases also don't break when unanticipated popups appear as they are taken care of by Watchers.\\